\section{Verification of model accuracy}
The results outlined above only consider the learning process.
However for our optimisations to be considered successful, we need to compare the accuracy of the initial serial implementation of the model with the current parallelised implementation.


\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        Version & Learned Weights   & Handset Weights   & Random Weights    \\\hline
        CPU     & 63.70\%           & 62.33\%           & 19.37\%           \\\hline
        GPU     & 41.93\%           & 67.27\%           & 19.37\%           \\\hline
    \end{tabular}
    \caption{
        Table comparing the accuracy of the model with respect to a 3000 step walk in the plus maze for each type of learning method, using handset weights, learned weights and random weights.
    }
    \label{tab:res_Metrics}
\end{table}

\tableref{tab:res_Metrics} shows the accuracy of the model for both the original CPU implementation and our parallelised implementation.
We consider 3 types of weights, weights learned from our learning process, handset weights of the model and random initialisation of weights.
For the random initialisation of weights there is no change in accuracy. 
This is due to the seed for initialising the weights being the same across both models.

With the handset weights, our implementation shows an overall increase of 5\% in Accuracy.
This suggests that the parallelised model obtains a more accurate picture of it's environment when given a good starting weight value for each area of the model.
However there is a loss of 20\% accuracy when using learned weights from the learning process.
This implies that there is an error in our learning process that affects the overall accuracy.

The next step from this is to add unit tests to both the learning and the evaluation process.
These tests would be targeted to capture the behaviour which causes the learned accuracy to be reduced.
This would allow the problem to be investigated and fixed, and would improve the accuracy to being approximately the same as the initial, CPU version.
